### 2016-05-04 abstract.tex
Add the problem statement to summary

>>>>

Object orientation provides principles for abstraction and encapsulation.
Abstraction is accomplished by high-level concepts of interfaces, classes, and objects (class instances).
Many object-oriented languages have followed the blocking and synchronous model of messaging. 
One of the fundamental elements of the actor model is \emph{asynchronous} message passing.
However, a message is not bound to any interface in the actor model.
It has been an ongoing research to combine object-oriented programming with the actor model.
Multicore and distributed computing raised a new challenge: combining object orientation, the actor model, and \emph{concurrency}.
In a concurrent setting, coroutines enable interactions with collaborative pre-emption.
Coroutines are not originally established in the object-oriented paradigm.
In a concurrent setting with objects, multi-threading has been a common approach to provide an object-oriented concurrency model.
Furthermore, interactions in both coroutines and multi-threading are blocking and synchronous.
In contrast, the actor model relies on asynchronous communication.
While a message is processed, an actor cannot be pre-empted or intentionally yield to allow other actors in the system to make progress.
Integration of actor model and object orientation leads to the use of asynchronous method calls.
